---
title: "Intro to the {lifecycling} R package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Intro to the {lifecycling} R package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(lifecycling)
```

The {lifecycling} R package acts as a repository to demonstrate several concepts 
and packages around versioning and lifecycle documentation. It is aimed at R 
package development but many of the topics covered apply to other areas of 
software development, such as semantic versioning.

For a full explanation of the concepts see the [other vignette](https://joshwlambert.github.io/lifecycling/articles/comm_code_dev.html) 
in this package.

The {lifecycling} package provides no novel functionality, and the functions 
exported as part of this package are wrapper to explore the functionality of the 
{lifecycle} R package from tidyverse, see <https://lifecycle.r-lib.org/> for more
information.


